Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-11 ms.tex
Modify Section 2
From 2e7b1a2:
============

In ms.tex,

(*) Modify Section 2

The defining characteristics of the {\it pitchfork} signature are understood as follows. The steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits in wide-field measurements. This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths.

Detailed modeling presented in Paper~I has important implications for future instrument design and analysis algorithms:
\begin{enumerate}
\item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
\item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity away from the primary field of view. 
\end{enumerate}

In this paper, we confirm this key feature using deeper data from the MWA.

>>>>

The defining characteristics of the {\it pitchfork} signature are understood as follows. The steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits in wide-field measurements. This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths. In this paper, we confirm this key feature using deeper data from the MWA.

% Detailed modeling presented in Paper~I has important implications for future instrument design and analysis algorithms:
% \begin{enumerate}
% \item positioned adjacent to the Fourier modes most sensitive to the cosmological signal, the {\it pitchfork} feature is a leading source of contamination in these modes, and 
% \item of the cases considered, a dish-shaped antenna was found to yield the most desirable response from a foreground contamination viewpoint due to a relatively efficient suppression of sensitivity away from the primary field of view. 
% \end{enumerate}
